Computer Science House By-Laws

### 2019-03-01 articles.tex
Remove the notarize reference
We don't require this per the constitution

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc.
%  However, if a sub part is moved to a different part, its references must be
%  changed.
% -This document must be ratified by the House (as per the Constitution),
%  then printed, signed, notarized, and placed in the House filing cabinet
%  if changes are to be officialized.

@@

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
House will also help to reacclimate any returning member back to the culture of House upon their return.
Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.
A member is also allowed to be physically present and also be on a leave of absence.
\asubsection{Leave of Absence Request}
A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
The request is then given to a staff member of Residence Life, excluding student employees, for approval.
A leave of absence start date can be backdated.
At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
\asubsection{Leave of Absence Duration}
A leave of absence can be granted for up to the length of one semester.
\asubsection{Leave of Absence Extension}
A leave of absence can be extended by submitting a new request.
\asubsection{Leave of Absence Return}
A member may return from a leave of absence whenever they choose to.
When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
\asubsection{Modified Evaluations}
A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
\asubsection{Leave of Absence for an Executive Board Member}
The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
Upon returning, the member may assume their position and the interim director is removed.
If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amongst the Executive Board to require a resignation from the Member.

@@

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
	\item To meet, as an Executive Board, at least weekly during the Standard Operating Session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
	\item To report pertinent information to House members at the following House Meeting
	\item To maintain records of the goals defined by each previous Executive Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
	\item To review and update the Constitution at the end of each Standard Operating Session, as defined in \ref{Standard Operating Session}
		The constitution should remain up to date with current practices.
\end{enumerate}

>>>>

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc.
%  However, if a sub part is moved to a different part, its references must be
%  changed.
% -This document must be ratified by the House (as per the Constitution),
%  if changes are to be officialized.

@@

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
House will also help to reacclimate any returning member back to the culture of House upon their return.
Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.
A member is also allowed to be physically present and also be on a leave of absence.
\asubsection{Leave of Absence Request}
A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
The request is then given to a staff member of Residence Life, excluding student employees, for approval.
A leave of absence start date can be backdated.
At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
\asubsection{Leave of Absence Duration}
A leave of absence can be granted for up to the length of one semester.
\asubsection{Leave of Absence Extension}
A leave of absence can be extended by submitting a new request.
\asubsection{Leave of Absence Return}
A member may return from a leave of absence whenever they choose to.
When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
\asubsection{Modified Evaluations}
A member may request their evaluation period to be extended by the duration of the leave or to end of the standard operating session, whichever comes first.
\asubsection{Leave of Absence for an Executive Board Member}
The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
Upon returning, the member may assume their position and the interim director is removed.
If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amongst the Executive Board to require a resignation from the Member.

@@

\asection{Responsibilities}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\asubsection{Responsibilities of the Executive Board}
\begin{enumerate}
	\item To hold a weekly meeting specific to their responsibilities and submit notes to the House
	\item To meet, as an Executive Board, at least weekly during the standard operating session, as defined in \ref{Standard Operating Session} to discuss and report the operations of the House
	\item To report pertinent information to House members at the following House Meeting
	\item To maintain records of the goals defined by each previous Executive Board
	\item To act as a Judicial Board as defined in \ref{Judicial}
	\item To review major projects, as defined in \ref{Expectations of House Members}, presented to them by the Evaluations director
	\item To make the final vote regarding conditionals and appeals as defined in \ref{Membership Evaluation}
	\item To respect the privacy of House members confiding in the Executive Board, barring situations related to endangerment of oneself or others, sexual assault, or in the case of a Judicial Board
	\item To publish a document at the end of each semester to all Members stating House’s accomplishments of that semester
	\item To review and update the Constitution at the end of each standard operating session, as defined in \ref{Standard Operating Session}
		The constitution should remain up to date with current practices.
\end{enumerate}

### 2019-03-01 bylaws.tex
Remove the notarize reference
We don't require this per the constitution

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc.
%  However, if a sub part is moved to a different part, its references must be
%  changed.
% -This document must be ratified by the House (as per the Constitution),
%  then printed, signed, notarized, and placed in the House filing cabinet
%  if changes are to be finalized.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems.
Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 75\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}

>>>>

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc.
%  However, if a sub part is moved to a different part, its references must be
%  changed.
% -This document must be ratified by the House (as per the Constitution),
%  if changes are to be finalized.

@@

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems.
Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
